A quantitative framework for investigating the reliability of network construction

### 2018-06-07 manuscript/CI_interactions.tex
81 words too many

    \item  Descriptions of ecological networks typically assume that the same interspecific interactions occur each time a community is observed. This contrasts with the known stochasticity of ecological communities: community composition, species abundances, and link structure all vary in space and time. Moreover, finite sampling generates variation in the set of interactions actually observed. 
    \item Here we develop the conceptual and analytical tools needed to capture uncertainty in the estimation of pairwise interactions. To define the problem, we identify the different contributions to the uncertainty of an interaction and its implications for the estimation of network properties. We then outline a framework to quantify the uncertainty around each interaction. We illustrate this framework using the most extensively sampled network to date. 
    \item We found significant uncertainty in estimates for the probability of most pairwise interactions which we could, however, limit with informative priors. This uncertainty scaled up to summary measures of network structure such as connectance or nestedness. Even with informative priors, our results suggest that the relatively well-sampled network we use as a test case is missing many interactions that may occur rarely or under different local conditions. 
    \item Through these efforts, we demonstrate the utility of our approach and the importance of acknowledging the uncertainty inherent in network studies. Most importantly, we stress that networks are best thought of as systems constructed from random variables, the stochastic nature of which must be acknowledged for an accurate representation. Doing so will fundamentally change networks analyses and yield greater realism.
  % Can be up to 350 words for MEE. This is 200 exactly.
\end{enumerate}

@@

          First, and most fundamentally, we do not know whether or not a pair of species have the appropriate characteristics (or traits) to interact. We define the probability of an interaction $L$ given characteristics $\mathbf{T}$ as $P(L | \mathbf{T})=\lambda$. If two species have incompatible traits, they may not interact even if there are no other constraints (e.g., temporal separation of species, inability to detect cryptic species) preventing the interaction from being observed. As a simple example, a prey species may be too large to be consumed by a predator. In such cases, $\lambda$ would take a value of 0 and there would be no uncertainty.

          Based on an observed network, however, it is often unclear whether an unobserved interaction is impossible due to incompatible traits or simply a rare phenomenon with $\lambda>0$. This uncertainty is partly addressed by trait-matching models~\citep{Bartomeus2016}. Nevertheless, every model is imperfect and lacks information that could be used to define constraints on interactions~\citep{Dormann2017}. Some interaction uncertainty therefore remains in current trait-matching models. As more information about the influence of traits on interactions is uncovered, this uncertainty is likely to be reduced and $\lambda$ should either tend to 0 or to 1.

@@

@@

          Lastly, measurement errors are a pervasive source of uncertainty in the observation of ecological processes. Given that an interaction is feasible and occurs under the local conditions ($L$=1 and $X$=1), we may define the detection of an interaction, $D$, as a stochastic process with the associated probability $P(D|X=1,L=1)=\delta$. Detection failure could happen for many reasons (see~\citet{Wirta2014} for examples of these difficulties and partial solutions to them). Some sources of detection error can be minimised with appropriate sampling effort ($\delta$ will converge to one with increasing number of samples), but other sources are often difficult to reduce (e.g. the occurrence of cryptic species might require molecular analysis for appropriate taxonomic identification as in~\citealt{Wirta2014,Frost2016}).

@@

        An observed interaction indicates that an interaction was feasible, occurred at the study site during sampling, and was detectable. That is, $L = 1$, $X = 1$, and $D = 1$. An unobserved interaction could be due to any of the three sources of uncertainty ($D$, $X$, and/or $L = 0$). Only the case where $L = 0$ is a true absence of interaction --the usual interpretation of a $0$ value in an interaction matrix. It is particularly important to rule out the situations where $D=0 \cup X = 1 \cup L=1$, i.e. where the interaction occurred at the location but was not observed, and $X = 0 \cup L =1$, i.e., where the interaction is feasible but did not occur at the local site. 
        % The occurrence of a true absence, our quantity of interest, corresponds to the joint event $L=0 \cup X=1 \cup D=1$ but %% AC: Doesn't a true absence just mean $L=0$ regardless of our ability to detect/local conditions? 
        Using empirical data, however, it is impossible to distinguish between sources of variation. An empirical ecologist will measure the marginal probability $P(L) = k/n$, where $k$ is the number of observed interactions and $n$ the number of observed co-occurrences. This probability does not contain any information about $D$ or $X$.

        The considerations above raise major challenges: when faced with empirical data, how may we infer whether unobserved interactions truly do not occur? How may we refine our sampling approaches to reduce uncertainties and gain insights into the impact of multiple processes on field observations? Importantly, some sources of uncertainty within these three broad groupings can be minimised with appropriate sampling (e.g., sampling in a variety of weather conditions, combining different methods of detection) while other sources are difficult or impossible to reduce since they are generated by the process in which we are interested (e.g., variation in individual preferences or traits). Given this multifaceted problem of uncertainty, what can we do to separate the different types of variation and reduce those that can be reduced?

        When attempting to reduce uncertainty, the obvious rule of thumb is to ``sample more" (Fig.~\ref{upper_limits}). Increasing sample sizes will reduce uncertainty about the upper bound of the interaction probability and will also increase the probability of detecting unlikely or cryptic interactions (e.g., interactions where $L$=1 but process or detection uncertainty is high). Despite these benefits, we note that there are limits to the utility of increased sampling. Since the probability of observing the co-occurrence of two species will always be higher than the probability of observing their interaction (since the probability of interaction is conditional on both interaction partners being present), we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions (Fig.~\ref{histograms}C). Thus, the more we sample, the more zeros will appear in our interaction matrix.

@@

        A slight variation on the theme of ``sample more" is to sample repeatedly. In one endeavour to uncover the cause of unobserved interactions,~\citet{Weinstein2017} used repeated sampling rounds to estimate the daily probability of detecting an interaction and thereby model detection and process uncertainty. While conceptually attractive, this approach is unsuitable for interactions occurring over longer time scales (e.g., associations between hosts and parasitoids with a single generation per year), or very rare interactions which might not occur on any of the sampling days. Worse, the problem persists that the absence of an interaction on a given day could be because it was impossible on that day despite being otherwise feasible [$P(X|L=1)=0$], because interaction did occur but could not be observed [$P(D|X=1,L=1)=0$]. From a conceptual perspective, this approach therefore fails to satisfactorily distinguish between sources of uncertainty.

        Most importantly, if two species are never observed co-occurring during several days of sampling then repeated sampling reveals nothing about their probability of interacting if they should ever co-occur. The bottom line is that separating different sources of uncertainty is difficult indeed. Nevertheless, we propose that information on the probability of detecting interactions in a focal system can be obtained by combining repeated sampling with prior information from the same or a similar system. Here, we first outline the statistical framework for a Bayesian approach to probabilistic interactions and then illustrate this approach with an intensively and repeatedly sampled empirical dataset.

@@

  \subsection*{A naive quantification of uncertainty}

    We start by considering how to naively quantify an interaction probability and its associated uncertainty \emph{for an interaction that has not yet been observed}. Consider the case where a pair of species have been observed co-occurring $n$ times, of which they have been observed to interact in $k = 0$ cases. To evaluate the uncertainty of this interaction, consider the occurrence of an interaction as a Bernoulli trial. In this framework, the number of successes $k$ over $n$ trials will follow a binomial distribution:

        \begin{equation}
          L \sim Bin(n,\lambda) ,
        \end{equation}

        \begin{equation}
           P(L = k|\lambda,n) = {n \choose k}\lambda^k(1-\lambda)^{n-k} . 
           \label{likelihood}
        \end{equation}

    \noindent The parameter $\lambda$, the probability of observing an interaction over an infinite time interval and area, is the quantity we want to estimate from empirical data. 
    The maximal likelihood estimate (MLE) of $\lambda$ is straightforward to find given $k$ and $n$:

@@

    All of the above methods for estimating the variance of $\lambda$ include the number of samples $n$. This means that where the number of samples $n$ is very low, as for rare species, there will be considerable uncertainty around our estimate of $\lambda$. In Fig.~\ref{upper_limits}, we derive the Clopper-Pearson interval to explore how the estimate of $\lambda$ varies with sample size. At a small sample size, the 95\% confidence interval spans all values of $\lambda$. To establish that species are not interacting with any acceptable certainty requires tens of observations of the two species co-occurring but not interacting. As most data sets will lack such extensive sampling across all species pairs, we can use a Bayesian approach to supplement the data we have with other sources of information.

  \subsection*{Inferring interaction probabilities}

      \subsubsection*{Posterior distribution of the interaction probability}

        Here we adopt a Bayesian approach to estimate the posterior distribution of the parameter $\lambda$ :

        \begin{equation}
          \underbrace{P(\lambda|k,n)}_{Posterior} = \frac{\overbrace{P(k|\lambda,n)}^{Likelihood}\overbrace{P(\lambda)}^{Prior}}{\underbrace{P(k|N)}_{Normaliser}} .
          \label{posterior}
        \end{equation}

        According to the above description, the likelihood is simply the binomial distribution (Eq.~\ref{likelihood}). Since $\lambda$ is a probability, it is bounded between 0 and 1 and the most appropriate prior distribution is the beta:

@@

       The beta-binomial distribution is a conjugate distribution of the binomial distribution. This allows us to analytically compute the posterior distribution of a binomial model with a beta prior distribution. We can re-write the posterior distribution of $\lambda$ as:

        \begin{equation}
          P(\lambda|k,n) = \frac{\lambda^{\alpha+k-1}(1-\lambda)^{\beta+n-k-1}}{B(\alpha+k,\beta+n-k)} , \label{posterior2}
        \end{equation}

        \noindent where the function $B$ is the beta function. The posterior distribution of $\lambda$ therefore follows the beta distribution with new parameters $\alpha'= \alpha+k$ and $\beta'=\beta+n-k$. The weight of the prior on the posterior distribution can be understood from these parameter definitions: the difference between the posterior and the prior will increase with $k$ and $n-k$. In other words, the distribution of $\lambda$ for better-sampled pairs of species will rely less on the information used to build the prior distribution and depend more on the observed data.
        When plotted, we find the shape of the distribution gets narrower with $k$ and $n$ (Fig.~\ref{Salix_pdfs_cdfs}).

@@

      \subsubsection*{The prior distribution}

        Parameters $\alpha$ and $\beta$ determine the shape of the prior distribution of $\lambda$, which follows a beta distribution. These are called hyper parameters. The prior may be chosen to be uninformative, if no external information is available, or may draw on information such as distributions of connectance across webs, degree within webs, or a trait-matching function (see \emph{Appendix S1} for details and a simple quantitative example).

\subsection*{Scaling up to networks - an empirical example}

    In the following section, we will provide an empirical example based on the well-sampled system of willow (\emph{Salix}) species, herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}. This dataset consists of a single community type sampled across Europe over 29 years and at 374 unique locations. The data were collected over 29 years at 374 unique locations across Europe. The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes (see \emph{Appendix S2} for details).

    The high spatiotemporal resolution of this network and the unusually high sampling effort implemented at the site level makes this dataset particularly well suited for illustrating the difficulties in completely sampling a network and testing Bayesian approaches to overcome these difficulties. To do this, we first compared the frequencies of observed co-occurrences and interactions. We analysed both the \emph{Salix}-galler and galler-natural enemy components of the network but, for the sake of brevity, present only the latter here. For the \emph{Salix}-galler component see \emph{Appendix S3}.

  \subsection*{Computing the prior and posterior distributions}

      In a strict Bayesian framework, we wish to use a prior distribution that does not rely on any information from the study at hand. Network data for a similar study system may, however, not be available. In that case, one might use the first sub-network collected as ``training data" to guide future sampling. To simulate this situation, we created priors using a single sub-network from the middle of the geographical distribution of the~\citet{Kopelke2017} dataset. To demonstrate how the use of data from a different system can affect the prior distribution and conclusions based on it, we repeated our analyses using priors derived from a much smaller \emph{Salix}-galler-natural enemy system~\citep[Data available from the Dryad Digital Repository: https://doi.org/10.5061/dryad.g7805]{Barbour2016}\nocite{Barbour2016Dryad}. This smaller system was much more densely-connected than that described in~\citet{Kopelke2017} and provided unreasonable distributions for interaction probabilities (\emph{Appendix S4}).

      To obtain the priors based on the Zillis sub-network, we estimated frequencies of interactions based on the normalised degree of each species in each network component
      (see \emph{Appendix S5} for details and code). Using these prior parameters, we then estimated the posterior distributions of interaction probabilities $\lambda$. For species without observed interactions ($n = 0$), the posterior distribution is identical to the prior distribution. For species where $n>0$, we can update the prior distribution with data. If we consider only pairs of species which were observed to co-occur but not to interact, $k_{ij}$ is always 0 and only $n_{ij}$ will vary between species pairs. This gives $\alpha'$=$\alpha$ and $\beta'$=$\beta + n_{ij}$. We calculated posterior distributions and 95\% credible intervals (see function ``credible\_interval" in \emph{Appendix S6}) for species with $n$ ranging between 0 and 374, the total number of sites in our dataset.

  \subsection*{How many samples are required to reach a minimal precision}

      Rather than calculating credible intervals for a posterior distribution after collecting data, we may wish to know how many data points are necessary to obtain a given level of confidence that two co-occurring species do not interact. The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact (Fig.~\ref{Salix_pdfs_cdfs}; see function samples\_for\_threshold in~\emph{Appendix S6}). The number of samples required to be 95\% confident that the interaction probability between galler and natural enemy species is below a threshold increases quickly as the threshold decreases (\emph{Appendix S7}). The 95\% credible interval is (\textless0.001, 0.303) for the probability of interaction between two species observed to co-occur but never interact. To be 95\% confident that the probability of interaction is below 0.1, 0.05, or 0.01 would require 15, 39, and 229 observed co-occurrences, respectively.

      Given the low levels of replication in most network studies, this implies that we should have fairly low confidence in many ``non-interacting" pairs of species. Even in the extensively replicated \emph{Salix}-galler-natural enemy dataset, very few species pairs were observed co-occurring frequently enough to reach these thresholds.  Regardless of our choice of prior, no species pairs were observed to co-occur frequently enough to reach the threshold for an interaction probability of 0.01. Discounting potential interactions, then, requires either a stronger prior expectation of no interaction (e.g. for forbidden interactions) or very extensive sampling. For all we know, most links absent from current descriptions of network structure may be so not because the species do not interact, but because we have not sampled deeply enough to detect them.

  \subsection*{Scaling up to network metrics}

@@

  \subsection*{Computing the prior and posterior distributions}

      We obtained prior parameters of $\alpha$=0.700, $\beta$=8.49. Where $n = 0$, these parameters gave a posterior distribution with $\bar\lambda$=0.076, var($\lambda$)=0.008. The posterior interaction probabilities obtained based on the Zillis sub-network were much lower than those obtained based on~\citet[Data available from the Dryad Digital Repository: https://doi.org/10.5061/dryad.g7805]{Barbour2016}; this emphasises the importance of using an appropriate study system when constructing a prior (\emph{Appendix S4}). When $n = 374$, we obtained a posterior distribution with $\bar\lambda_{ij}$=1.83 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=4.76. This distributions is very close to 0 with small variance about $\lambda$; species $i$ and $j$ are extremely unlikely to interact at sites or times not included in our sample.

      For most pairs of species $i$ and $j$, however, $n_{ij}$ was much less than 374 and our posterior mean and variance therefore retain more of the influence of the prior. We can see this in the increasing means and variances as we decrease $n_{ij}$ (Fig.~\ref{Salix_pdfs_cdfs}). The change in distribution as $n_{ij}$ decreases can also be shown  by calculating 95\% credible intervals for $\lambda$ (see the function ``credible\_interval" in \emph{Appendix S6}). The 95\% credible interval for hypothetical galler-natural enemy pairs, meanwhile, widened from (0.00001, 0.008) to (0.0005, 0.304).

  \subsection*{How many samples are required to reach a minimal precision}

  \subsection*{Scaling up to network metrics}

@@

  Even in the most extensive data set that we could find, there was very little empirical data for each species pair. Most pairs of species were not observed co-occurring even once, and less than 10\% of species pairs were observed interacting. This suggests that limited sampling is a major source of uncertainty in all empirical networks. This dataset also illustrates the problem of process uncertainty - pairs of species which were observed to interact did not interact in all of the samples in which they co-occurred. The number of observed co-occurrences strongly affected the posterior distribution of $\lambda$, meaning that our level of confidence that an interaction probability is below some threshold depends strongly on the amount of information available for each pair of species.

  [[Recap results]]

  Real interaction networks vary over several dimensions~\citep{Kitching1987,Olesen2011a,Pires2011a,Baiser2012,Fodrie2015,Novak2015} and to capture this variation we must turn from static descriptions of network structure to probabilistic descriptions. In this study, we have developed the analytical tools to capture the uncertainty in the estimation of pairwise interactions and a conceptual framework for its individual components: interaction uncertainty, process uncertainty, and detection uncertainty. Using this framework leads us to offer tangible recommendations for improved descriptors of ecological interactions. First, our analyses point to detection uncertainty as a major contributor to overall uncertainty of is establishing the absence of interaction. To counter this and establish true absences of interactions requires comparatively large sample size – on the order of 30-50 observations per species pair. Second, where such extensive sampling is not feasible, researchers should still acknowledge the varying levels of confidence surrounding the presence or absence of interactions between different pairs of species. Including the $n$ and $k$ values for each interaction will clearly indicate which unobserved interactions are most likely to be observed with further sampling and which estimates are more reliable. Third, the uncertainty around interactions (especially interactions that were not observed) should be incorporated in calculations of network properties like connectance or nestedness. Re-sampling networks based on a probabilistic understanding of networks is straightforward and gives distributions for network properties rather than point estimates. This not only acknowledges the fact that interactions vary over time and space but will also facilitate comparisons between networks. With confidence intervals around network metrics, we can not only say that one network is more connected than another but also whether the networks are more different than we would expect based on imperfect sampling of interactions. To facilitate these recommendations, we provide all code used in this paper in the supplementary material.

>>>>

    \item  Descriptions of ecological networks typically assume that the same interspecific interactions occur each time a community is observed. This contrasts with the known stochasticity of ecological communities: community composition, species abundances, and link structure all vary in space and time. Moreover, finite sampling generates variation in the set of interactions actually observed. For interactions that have not been observed, most data sets will not contain enough information to be confident that unobserved interactions truly did not occur.
    \item Here we develop the conceptual and analytical tools needed to capture uncertainty in the estimation of pairwise interactions. To define the problem, we identify the different contributions to the uncertainty of an interaction. We then outline a framework to quantify the uncertainty around each interaction by combining data on observed co-occurrences with prior knowledge. We illustrate this framework using the most extensively sampled network to date. 
    \item We found significant uncertainty in estimates for the probability of most pairwise interactions which we could, however, limit with informative priors. This uncertainty scaled up to summary measures of network structure such as connectance or nestedness. Even with informative priors, our results suggest that the extremely well-sampled network we use as a test case is missing many interactions that may occur rarely or under different local conditions. 
    \item Through these efforts, we demonstrate the utility of our approach and the importance of acknowledging the uncertainty inherent in network studies. Most importantly, we stress that networks are best thought of as systems constructed from random variables, the stochastic nature of which must be acknowledged for an accurate representation. Doing so will fundamentally change networks analyses and yield greater realism.
  % Can be up to 350 words for MEE. This is 270 exactly.
\end{enumerate}

@@

          First, and most fundamentally, we may not know whether or not a pair of species have the appropriate characteristics (or traits) to interact. We define the probability of an interaction $L$ given characteristics $\mathbf{T}$ as $P(L | \mathbf{T})=\lambda$. Some species pairs, such as a salmon and a saguaro cactus, have incompatible traits and would never interact even if they should co-occur. In such cases, $\lambda = 0$ and there is no uncertainty.

          Most species pairs, however, do not have traits that absolutely prevent an interaction. This means that it is generally unclear whether an unobserved interaction is impossible or simply a rare phenomenon with $\lambda>0$. This uncertainty is partly addressed by trait-matching models in which species with better-matched traits are more likely to interact~\citep{Bartomeus2016}. As these models improve and include better information about the influence of traits on interactions, the uncertainty will be reduced and $\lambda$ should either tend to 0 or to 1. Nevertheless, every model is imperfect and lacks information that could be used to define constraints on interactions~\citep{Dormann2017}. Some interaction uncertainty will remain even using a very good trait-matching model.

@@

         One proposed solution to the problem of process uncertainty is to use repeated sampling of networks. For example,~\citet{Weinstein2017} used repeated sampling rounds to estimate the daily probability of detecting an interaction and thereby model detection and process uncertainty. While conceptually attractive, this approach is unsuitable for interactions occurring over longer time scales (e.g., associations between hosts and parasitoids with a single generation per year), or very rare interactions which might not occur on any of the sampling days. Moreover, the faster accumulation of species than interactions means that repeated sampling will tend to introduce more unobserved interactions than observed interactions unless the number of samples is very high~\citep{Poisot2012}.

@@

          Lastly, measurement errors are a pervasive source of uncertainty in the observation of ecological processes. That is, even if an interaction is feasible and occurs during sampling ($L = 1$ and $X = 1$), we may fail to detect it. We may define the probability of detecting of an interaction, $D$, as a stochastic process with the associated probability $P(D|X=1,L=1)=\delta$. Detection failure could happen for many reasons (see~\citet{Wirta2014} for examples and partial solutions to them). Some sources of detection error can be minimised with appropriate sampling effort ($\delta$ will approach one with increasing number of samples), but other sources are often difficult to reduce (e.g. the occurrence of cryptic species might require molecular analysis for appropriate taxonomic identification as in~\citealt{Wirta2014,Frost2016}). The impossibility of eliminating detection uncertainty also limits the usefulness of repeated sampling; the absence of an interaction on a given day could either be because it was not feasible [$P(L) = 0$], was feasible but did not occur because of local conditions during sampling ($P(X|L=1) = 0$], or was feasible and occurred during sampling but could not be observed [$P(D|X=1,L=1)=0$]. From a conceptual perspective, repeated sampling therefore fails to satisfactorily address the uncertainty inherent in empirical networks.

@@

        An observed interaction indicates that an interaction was feasible, occurred at the study site during sampling, and was detectable. That is, $L = 1$, $X = 1$, and $D = 1$. An unobserved interaction could be due to any of the three sources of uncertainty ($D$, $X$, and/or $L = 0$). Only the case where $L = 0$ is a true absence of interaction --the usual interpretation of a $0$ value in an interaction matrix. It is particularly important to rule out the situations where $D=0 \cup X = 1 \cup L=1$, i.e. where the interaction occurred at the location but was not observed, and $X = 0 \cup L =1$, i.e., where the interaction is feasible but did not occur at the local site (Fig.~\ref{concept_fig}). 
        % The occurrence of a true absence, our quantity of interest, corresponds to the joint event $L=0 \cup X=1 \cup D=1$ but %% AC: Doesn't a true absence just mean $L=0$ regardless of our ability to detect/local conditions? 
        Using empirical data, however, it is impossible to distinguish between sources of variation. An empirical ecologist will measure the marginal probability $P(L) = k/n$, where $k$ is the number of observed interactions and $n$ the number of observed co-occurrences. This probability does not contain any information about $D$ or $X$. The major question then becomes: how can we reduce the uncertainty around our estimated interaction probability?

        % The considerations above raise major challenges: when faced with empirical data, how may we infer whether unobserved interactions truly do not occur? How may we refine our sampling approaches to reduce uncertainties and gain insights into the impact of multiple processes on field observations? Importantly, some sources of uncertainty within these three broad groupings can be minimised with appropriate sampling (e.g., sampling in a variety of weather conditions, combining different methods of detection) while other sources are difficult or impossible to reduce since they are generated by the process in which we are interested (e.g., variation in individual preferences or traits). Given this multifaceted problem of uncertainty, what can we do to separate the different types of variation and reduce those that can be reduced?

        When attempting to reduce uncertainty, the obvious rule of thumb is to ``sample more". Increasing sample sizes will reduce uncertainty about the upper bound of the interaction probability and will also increase the probability of detecting unlikely or cryptic interactions (e.g., interactions where $L$=1 but process or detection uncertainty is high). Despite these benefits, we note that there are limits to the utility of increased sampling. Since the probability of observing the co-occurrence of two species will always be higher than the probability of observing their interaction (since the probability of interaction is conditional on both interaction partners being present), we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions (Fig.~\ref{histograms}C). Thus, the more we sample, the more zeros will appear in our interaction matrix.

@@

        Most importantly, if two species are never observed co-occurring during several days of sampling then repeated sampling reveals nothing about their probability of interacting if they should ever co-occur. Intensive sampling is, therefore, an important step towards reducing uncertainty in ecological networks but is unlikely to be enough in most cases. To supplement repeated and intensive sampling efforts and further reduce uncertainty around unobserved interactions, we suggest researchers use prior information drawn from the same or a similar system. Here, we first outline the statistical framework for a Bayesian approach to probabilistic interactions and then demonstrate how to construct such a probabilistic network using an intensively and repeatedly sampled empirical dataset. Finally, we show how a probabilistic understanding of a network allows us to establish confidence intervals around measures of network structure.

@@

  \subsection*{A Bayesian framework for interaction probabilities}

    We are most interested in how to quantify an interaction probability, and its associated uncertainty, for an interaction that has not yet been observed. Say a pair of species has been observed co-occurring $n$ times and observed interacting in $k = 0$ cases. We want to know the probability $\lambda$ that the species would be observed interacting if not constrained by local conditions, timing, imperfect detection, etc. We can consider the occurrence of an interaction as a Bernoulli trail where the number of successes ($k$) over $n$ trials will follow a binomial distribution (see~\emph{Appendix S1} for a full description of the mathematical framework). In this framework, the maximum likelihood estimate (MLE) for $\lambda$ is:

@@

    All of the above methods for estimating the variance of $\lambda$ include the number of samples $n$. This means that where the number of samples $n$ is very low, as for rare species, there will be considerable uncertainty around our estimate of $\lambda$. In Fig.~\ref{upper_limits}, we derive the Clopper-Pearson interval to explore how the estimate of $\lambda$ (for true $\lambda = 0$) varies with sample size. At a small sample size, the 95\% confidence interval is nearly (0, 1). To establish that species are not interacting with any acceptable certainty requires tens of observations of the two species co-occurring but not interacting. Most data sets will lack such extensive sampling across all species pairs, but we can still use a Bayesian approach to supplement the available data with other sources of information.

    The Bayesian approach combines the MLE of $\lambda$ described above with a prior distribution and a normaliser to give a posterior distribution. For species pairs with a great deal of observed data (high $n$), the posterior distribution will mostly be based on the MLE of $\lambda$. Where there is little or no observed data (low $n$), the posterior distribution will reflect our prior knowledge. Since $\lambda$ is a probability and bounded between 0 and 1, the most appropriate prior distribution is the beta:

@@

    Combining the beta-distributed prior with the binomial-distributed MLE of $\lambda$ is straightforward (see~\emph{Appendix S1}). By doing so, we obtain a posterior distribution that follows a beta distribution with new parameters $\alpha'= \alpha+k$ and $\beta'=\beta+n-k$. The weight of the prior on the posterior distribution can be understood from these parameter definitions: the difference between the posterior and the prior will increase with $k$ and $n-k$. In other words, the distribution of $\lambda$ for better-sampled pairs of species will rely less on the information used to build the prior distribution and depend more on the observed data. When plotted, we find the shape of the distribution gets narrower with $k$ and $n$ (Fig.~\ref{Salix_pdfs_cdfs}).

@@

    \subsubsection*{Choosing a prior distribution}

      Parameters $\alpha$ and $\beta$ determine the shape of the prior distribution of $\lambda$, which follows a beta distribution. These are called hyper parameters. The prior may be chosen to be uninformative, if no external information is available, or may draw on information such as distributions of connectance across webs, degree within webs, or a trait-matching function (see \emph{Appendix S2} for details and a simple quantitative example).

      When using an informative prior, it is important to ensure that the prior accurately reflects the focal  system. For example, if the focal system is a large network containing many plant species and insects from different families, it is inappropriate to use a prior distribution drawn from a small network describing interactions between different genotypes of a single plant species wtih a set of closely-related insects. The similarity of traits for genotypes within a species means that an insect which interacts with one genotype is likely to interact with many others. Trait differences between species means that a species-species network will likely contain fewer interactions than a genotype-species network. Similarly, highly-aggregated networks containing nodes which represent whole classes or families are likely to have very different structures than networks where most nodes represent single species.

      The choice of prior will depend on the information available. In general, it is best to use a prior taken from a similar system. If such data are not available, a prior based on many networks systems with a similar level of resolution could be useful, as could a prior based on a preliminary round of sampling (analogous to ``training data"). If there is no suitable informative prior, it is best to use an explicitly uninformative prior. While an uninformative prior will not greatly reduce variance about $\lambda$, it does clearly state our lack of prior knowledge and will not bias our conclusions.

  \subsection*{An empirical example}

      We illustrate the process of constructing a Bayesian network using the well-sampled system of willow (\emph{Salix}) species, herbivorous gallers, and their natural enemies described by~\citet{Kopelke2017}. This dataset consists of a single community type sampled across Europe over 29 years and at 374 unique locations. The data were collected over 29 years at 374 unique locations across Europe. The meta-network consists of 1,173 different interactions between 52 \emph{Salix} nodes, 92 herbivore nodes, and 126 natural enemy nodes (see \emph{Appendix S3} for details).

      The high spatiotemporal resolution and unusally high sampling effort of this dataset make this it particularly well suited for illustrating the difficulties in completely sampling a network. To do this, we first compared the frequencies of observed co-occurrences and interactions. We analysed both the \emph{Salix}-galler and galler-natural enemy components of the network but present only the latter here (see~\emph{Appendix S4} for \emph{Salix}-galler results).

    \subsubsection*{Computing the prior and posterior distributions}

        A strict Bayesian framework requires a prior distribution that does not rely on any information from the study at hand. If such data are not available, one might instead use the first sub-network collected as ``training data" to guide future sampling. To simulate this situation, we created priors using a single sub-network from the middle of the geographical distribution of the~\citet{Kopelke2017} dataset. To demonstrate how the use of data from a different system can affect the prior distribution and conclusions based on it, we repeated our analyses using priors derived from a much smaller \emph{Salix}-galler-natural enemy system based around genotypes of a single \emph{Salix} species~\citep[Data available from the Dryad Digital Repository: https://doi.org/10.5061/dryad.g7805]{Barbour2016}\nocite{Barbour2016Dryad}. This smaller system was much more densely-connected than that described in~\citet{Kopelke2017} and provided unreasonable distributions for interaction probabilities (\emph{Appendix S5}).

        To obtain the priors based on the Zillis sub-network, we estimated frequencies of interactions based on the normalised degree of each species in each network component
        (see \emph{Appendix S6} for details and code). Using these prior parameters, we then estimated the posterior distributions of interaction probabilities $\lambda$. For species without observed interactions ($n = 0$), the posterior distribution is identical to the prior distribution. For species where $n>0$, we can update the prior distribution with data. If we consider only pairs of species which were observed to co-occur but not to interact, $k_{ij}$ is always 0 and only $n_{ij}$ will vary between species pairs. This gives $\alpha'$=$\alpha$ and $\beta'$=$\beta + n_{ij}$. We calculated posterior distributions and 95\% credible intervals (see function ``credible\_interval";~\emph{Appendix S7}) for species with $n$ ranging between 0 and 374, the total number of sites in our dataset.

        Rather than calculating credible intervals for a posterior distribution after collecting data, we may wish to know how many data points are necessary to obtain a given level of confidence that two co-occurring species do not interact. The number of samples needed will depend on both our desired level of confidence and the threshold below which we assume that two species are unlikely to ever interact. We calculated the number of samples required to reach 95\% confidence that $\lambda$ was below thresholds of 0.1, 0.05, and 0.01 as examples (see function ``samples\_for\_threshold";~\emph{Appendix S7}).

    \subsubsection*{Scaling up to network metrics}

@@

  We obtained prior parameters of $\alpha$=0.700, $\beta$=8.49. Where $n = 0$, these parameters gave a posterior distribution with $\bar\lambda$=0.076, var($\lambda$)=0.008. When $n = 374$, we obtained a posterior distribution with $\bar\lambda_{ij}$=1.83 $\times$ 10$^{-3}$, var($\lambda_{ij}$)=4.76. This distributions is very close to 0 with small variance about $\lambda$; species $i$ and $j$ are extremely unlikely to interact at sites or times not included in our sample.

  For most pairs of species $i$ and $j$, however, $n_{ij}$ was much less than 374 and our posterior mean and variance therefore retain more of the influence of the prior. We can see this in the increasing means and variances as we decrease $n_{ij}$ (Fig.~\ref{Salix_pdfs_cdfs};~\emph{Appendix S8}). The number of samples required to be 95\% confident that the interaction probability between galler and natural enemy species is below a threshold increases quickly as the threshold decreases (Fig.~\ref{Salix_pdfs_cdfs};~\emph{Appendix S8}). To be 95\% confident that the probability of interaction is below 0.1, 0.05, or 0.01 would require 15, 39, and 229 observed co-occurrences, respectively.

@@

  Real interaction networks vary over several dimensions~\citep{Kitching1987,Olesen2011a,Pires2011a,Baiser2012,Fodrie2015,Novak2015}, leading to pervasive under-estimation of interactions in published networks. Even in the most extensive data set that we could find, there was very little empirical data for each species pair. Most pairs of species were not observed co-occurring even once, and less than 10\% of species pairs were observed interacting and no pairs were observed to co-occur frequently enough to reach the threshold for an interaction probability of 0.01. This suggests that limited sampling is a major source of uncertainty in empirical networks. This dataset also illustrates the problem of process uncertainty - pairs of species which were observed to interact did not interact in all of the samples in which they co-occurred. This emphasizes the importance of accounting for imperfect detection when analysing empirical networks.

  Using prior knowledge to build a Bayesian distribution for each interaction probability allows us to treat unobserved interactions as less likely to occur while setting appropriate bounds on interaction probabilities between pairs of species which were never observed co-occurring. The number of observations required to conclude that an interaction is unfeasible is quite high (tens of observations per species pair); some species pairs are likely to fall short of this even in the highest-quality networks. In such cases, an informative prior distribution gives us more reasonable estimates of interaciton probabilities than assuming all unobserved interactions never occur. Moreover, interactions involving species entering new ranges due to climate change or introductions are important for a variety of conservation questions. A Bayesian approach using a trait-matching model or data from species' current ranges could be useful in anticipating how species will integrate into new communities.

  Our results also demonstrate how incomplete detection of interactions scales up to affect network structure. The structure of our well-sampled, replicated observed network is most similar to the structure of networks including only 50\% of the interactions suggested by the posterior distribution of interaction probabilities. Acknowledging the uncertainty inherent in a description of a system that is missing up to half of the feasible interactions is vital if we are to compare structures across systems, link structure to stability, etc.

  Using this framework leads us to offer tangible recommendations for improved descriptors of ecological interactions. First, sample sizes should be as large as possible in order to reduce detection uncertainty. Second, where sampling on the order of 30-50 observations per species pair is not possible (likely the bulk of studies), researchers should acknowledge the varying levels of confidence surrounding interactions between different species pairs. Including the $n$ and $k$ values for each interaction will clearly indicate which unobserved interactions are most likely to be observed with further sampling and which estimates are more reliable. Third, the uncertainty around interactions should be incorporated in calculations of network properties. Re-sampling networks based on a probabilistic understanding of networks is straightforward and gives distributions for network properties rather than point estimates. This not only acknowledges the fact that interactions vary over time and space but will also facilitate comparisons between networks by adding confidence intervals to estimates of network properties. This will allow us to say whether networks have different structures \emph{and} whether those differences are greater than we would expect given the inherent variability of interactions. To facilitate these recommendations, we provide all code used in this paper in the supplementary material.
